---
title: "accountR"
author: "Marie Lisanne Schürmann"
date: "Jun 30, 2022"
output:
  html_document:
    toc: true
    toc_depth: 2
  pdf_document:
    toc: true
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{accountR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(accountR)
```

# Introduction

The accountR package provides useful tools for accounting and financial reporting. The tools allow users to convert data frames that include values of multiple currencies automatically into one user-defined currency at a specific reporting date. Additionally, it provides functions to automatically generate a Trade Receivables Aged Analysis report which can be used to calculate the Allowance for Doubtful Accounts or other tasks of the Accounts Receivable Management, such as monitoring of payment collections.

# Setup

You must install the accountR library from CRAN or Github:

```{r}
#Installation from CRAN
#install.packages("accountR")

#or installation from Github
#library(devtools)
#install_github("mschuermann/accountR")
```

And then load it to use it in your session:

```{r}
library(accountR)
```

# Data

# Foreign Currency Conversion

# Trade Receivable Aged Analysis Report
